### 2015-04-17 src/intro/intro.tex
Minor updates

Life began about four billion years ago with the encapsulation of self-replicating RNA in a lipidic membrane \cite<e.g.>{orgel1968}. Simple as these probionts were, they did not have any means of locomotion and thus relied in full on the currents to deliver the nutrients required to replicate. As organisms evolved, they began to assert an increasing amount of control over their environment. A primitive example can be found in chemotaxis, where ciliae and flagellae, coupled with simple biochemical sensors allow the organism to follow biochemical gradients and thus actively gather nutrients.

Because flagellar motion is limited to either tumbles -- random reorientation movements -- or runs, the pathway linking these flagella to the biochemical sensors consists of only a few steps. With the advent of more advanced sensory and motoric systems, both the amount of information available to drive behaviour as well as the amount of possible behaviours available increased tremendously. As direct biochemical links between perception and action were no longer sufficient, simple neural network evolved to process the sensory signals allowing for abstract decisions about movement. Because organisms became more complex, these networks evolved into a complete (central) nervous system, culminating in the cerebral cortex.

In most higher organisms, including humans, the amount of data collected by the sensory organs is enormous, the visual system alone generating between $10^7$ and $10^9$ bits per second \cite{koch2006,kelly1962}. The nervous system, and the cerebral cortex in particular, seem to use probabilistic models to compress the vast amount of the incoming sensory data \cite{zhaoping2006}. The principal idea behind these models being that they reduce redundancy in the input by knowledge about the statistics of the natural world.

@@

\subsection{Vestibular system}

@@

\subsubsection{Otoliths}
The linear acceleration and gravitational forces are measured by the two otolith organs on either side of the head: the saccule and the utricule. Each otolith consists of an endolymph filled compartment containing calcium carbonate crystals known as otoconia (\panelref{intro:fig:otoliths}{A}). Due to their high inertia, these otoconia fall behind during linear acceleration (\panelref{intro:fig:otoliths}{B}), and move ahead during deceleration. In addition, they fall downward as a result of the gravitational field (\panelref{intro:fig:otoliths}{C}). The otoconia are mounted on top of a flexible polysaccharide gel, in which hair cells, similar to those found in the semicircular canals, are partly embedded \cite{goldberg2012}.

Einstein's equivalence principle states that  it is not possible to measure forces caused by linear acceleration and by gravity independently. The signal coming from the otoliths is therefore proportional to the combination of these forces \cite{fernandez1976b}, which is commonly referred to as the gravito-inertial force (GIF). Compared to the three semicircular canals, which are able to sense rotation in three dimensions due to their orthogonal organization, either side of the head only contains two otolith organs. It is still possible to sense the gravito-inertial force in three dimensions because the otolith organs are curved, and the orientation of the hair cells determined the direction of sensitivity \cite{goldberg2012}.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\panelref{intro:fig:vection}{A}) for example causes a different pattern than roll rotation (\panelref{intro:fig:vection}{B}). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when e.g. on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

In \citeyearNP{guedry1963}, \citeauthor{guedry1963} reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. Because of the VOR, eye movement in darkness are larger than those in the body-fixed condition. The underestimation in the body-fixed condition can therefore be interpreted as the involvement of eye movements, although the authors did not suggest this 
Studies on postural sway also indicate a role of eye movement is self-motion perception. Making eye movements causes postural sway to increase, suggesting that eye movements influence self-motion perception \cite{glasauer2005,rodrigues2015}.

One complication is that the magnitude, $e$, of these eye movements not only depend on the translation amplitude, $T$, but also on the fixation depth, $d$. Oculomotor cues to depth include binocular vergence angle and accommodation, both most robust for less fixations than a meter or so away. When fixating position $(x, d)$, the eye position at starting position is $e_0 = \arctan(d/x) \approx d/x$. By subtracting the eye position after the translation, $e_1 = \arctan(d/(x+T)) \approx d/(x+T)$, we obtain the eye movement amplitude, $e \approx d/T$. In \Chapter{p4} we explore whether the brain takes this geometry into account and compensates for fixation depth when using eye movements in self-motion perception. Fixation depth plays also a crucial role in \Chapter{p2}, in which the the effects of eye and head movements on spatial updating are investigated.

\section{Reflexive uses for the self-motion}
While vection is a valuable cue to self-motion perception, the brain wants to minimize vection because it blurs the image on the fovea, which hampers visual perception. Several reflexive mechanisms attempt to keep stable fixation to avoid image blurring during self-motion. Two such mechanisms are the vestibulo-ocular reflex, the VOR \cite{goldberg2012}, and the optokinetic reflex, the OKR \cite{purves2012}.

@@

\section{Integration of signals for action and perception}

@@

\subsection{Subjective body tilt}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference angle, e.g. 45\si{\degree}, and are then rotated to an angle close to the reference angle, e.g. 46\si{\degree} (see \panelref{intro:fig4}{A}). They then have to indicate whether their current orientation is clockwise or counter-clockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

@@

\subsection{Subjective visual vertical}
The subjective visual vertical, or SVV, task is a similar task in which participants have to judge the orientation of a line with respect to gravity. The PSE, that is the angle at which the line is perceived to be aligned with gravity, can be found by presenting lines at different angles and asking the participant whether the line is rotated clockwise or counter-clockwise relative to gravity (see \panelref{intro:fig5}{A}).

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect. At smaller angles overcompensation occurs and the static error is in the opposite direction, which is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR).

@@

We start with \Chapter{p1} in which we investigate sensory noise levels of the visual, somatosensory, and vestibular cues to head and body orientation. Because the contributions of these signals cannot be studied in isolation, we adopted an inverse approach where we assumed statistical optimality and attempted to compute the statistical properties of individual sensors. To this end, we fitted an optimal integration model to the behaviour from two psychophyisical tasks. The first gauged head-in-space orientation (SVV) and the second body-in-space orientation (SBT). The resulting estimates of the noise levels in the involved sensory modalities were used to predict the responses of patients with somatosensory and vestibular deficits. These predictions were consistent with previously published deficits in these patient groups, strengthening the idea that human spatial orientation is statistically optimal.

>>>>

Life began about four billion years ago with the encapsulation of self-replicating RNA in a lipidic membrane \cite<e.g.>{orgel1968}. Simple as these probionts were, they did not have any means of locomotion and thus relied in full on the currents to obtain the nutrients required to replicate. As organisms evolved, they began to assert an increasing amount of control over their environment. A primitive example can be found in chemotaxis, where ciliae and flagellae, coupled with simple biochemical sensors allow the organism to follow biochemical gradients and thus actively gather nutrients.

Because flagellar motion is limited to either tumbles -- random reorientation movements -- or runs, the pathway linking these flagella to the biochemical sensors consists of only a few steps. With the advent of more advanced sensory and motoric systems, both the amount of information available to drive behaviour as well as the amount of possible behaviours available increased tremendously. As direct biochemical links between perception and action were no longer sufficient, simple neural networks evolved to process the sensory signals allowing for abstract decisions about movement. Because organisms became more complex, these networks evolved into a complete (central) nervous system, culminating in the cerebral cortex.

In most higher organisms, including humans, the amount of data collected by the sensory organs is enormous, the visual system alone generating between $10^7$ and $10^9$ bits per second \cite{koch2006,kelly1962}. The nervous system, and the cerebral cortex in particular, seem to use probabilistic models to compress the vast amount of the incoming sensory data \cite{zhaoping2006}. The principal idea behind these models being that they reduce redundancy in the input by knowledge about the statistics of the natural world \cite{olshausen1996}.

@@

\subsection{Vestibular}

@@

\subsubsection{Otoliths}
The linear acceleration and gravitational forces are measured by the two otolith organs on either side of the head: the saccule and the utricule. Each otolith consists of an endolymph filled compartment containing calcium carbonate crystals known as otoconia (\panelref{intro:fig:otoliths}{A}). Due to their high inertia, these otoconia fall behind during linear acceleration (\panelref{intro:fig:otoliths}{B}), and move ahead during deceleration. In addition, they are pulled downward as a result of the gravitational field (\panelref{intro:fig:otoliths}{C}). The otoconia are mounted on top of a flexible polysaccharide gel, in which hair cells, similar to those found in the semicircular canals, are partly embedded \cite{goldberg2012}. These hair cells transform the shearing of the polysacchardige gel into a neural signal.

Einstein's equivalence principle states that  it is not possible to measure forces caused by linear acceleration and by gravity independently. The signal coming from the otoliths is therefore proportional to the combination of these forces \cite{fernandez1976b}, which is commonly referred to as the gravito-inertial force (GIF). Compared to the three semicircular canals, which are able to sense rotation in three dimensions due to their orthogonal organization, either side of the head only contains two otolith organs. It is still possible to sense the gravito-inertial force in three dimensions because the otolith organs are curved, and the orientation of the hair cells determines the direction of sensitivity \cite{goldberg2012}.

@@

\subsubsection{Vection}
When we move through the environment, the image of the world on our retina shifts. This large-field shift pattern, also known as optic flow, depends on the movement being made. Lateral translation (\panelref{intro:fig:vection}{A}) for example causes a different pattern than roll rotation (\panelref{intro:fig:vection}{B}). At the turn of the 19th century von Helmholtz \citeyear{vonhelmholtz1867} recognized the importance of these flow signals for self-motion perception. In some cases the optic flow signal is so strong that it causes a percept of self-motion in stationary participants, called vection \cite{dichgans1978}. This is experienced, for example, when sitting on the train and a neighbouring train starts to move. This effect is much less likely to occur when on the platform, suggesting that the vection signal is integrated with prior knowledge about the environment before causing self-motion perception \cite{andersen1985,lepecq1995}

@@

In \citeyearNP{guedry1963}, \citeauthor{guedry1963} reported a substantial underestimation of displacement when their observers watched a small body-fixed target compared to displacements in the dark. Because of the VOR, eye movement in darkness are larger than those in the body-fixed condition. The underestimation in the body-fixed condition can therefore be interpreted as the involvement of eye movements, although the authors did not suggest this. Studies on postural sway also indicate a role of eye movement is self-motion perception. Making eye movements causes postural sway to increase, suggesting that eye movements influence self-motion perception \cite{glasauer2005,rodrigues2015}.

One complication is that the magnitude, $e$, of these eye movements not only depend on the translation amplitude, $T$, but also on the fixation depth, $d$. Oculomotor cues to depth include binocular vergence angle and accommodation, which are both most robust for fixations less than a meter or so away. When fixating at Cartesian position $(x, d)$, the eye angle is $e_0 = \arctan(d/x) \approx d/x$. When translating the body, this angle becomes, $e_1 = \arctan(d/(x+T)) \approx d/(x+T)$. The eye movement amplitude is then, $e = e_1 - e_0 \approx d/T$. In \Chapter{p4} we explore whether the brain takes this depth dependent geometry into account and compensates for fixation depth when using eye movements in self-motion perception. Fixation depth plays also a crucial role in \Chapter{p2}, in which the effects of eye and head movements on spatial updating are investigated.

\section{Vestibular reflexes for the self-motion compensation}
While vection is a valuable cue to self-motion perception, the brain wants to minimize vection because it blurs the image on the fovea, which hampers visual perception. Several reflexive mechanisms attempt to keep stable fixation to avoid image blurring during self-motion. Two such mechanisms are the vestibulo-ocular reflex, the VOR \cite{goldberg2012}, and the optokinetic reflex, the OKR \cite{purves2012}.

@@

\section{Multisensory integration}

@@

\subsection{Body-tilt perception}
In the subjective body tilt, or SBT, task the perceived body orientation with respect to a given body tilt angle is probed. Participants are first given a reference angle, e.g. 45\si{\degree}, and are then rotated to an angle close to the reference angle, e.g. 46\si{\degree} (see \panelref{intro:fig4}{A}). They then have to indicate whether their current orientation is clockwise or counter-clockwise with respect to the reference angle. By systematically probing rotation angles around the reference angle we can obtain both the bias and uncertainty on the percept of body tilt.

@@

\subsection{Visual vertical perception}
The subjective visual vertical, or SVV, task is a similar task in which participants have to judge the orientation of a line with respect to gravity. The PSE, that is the angle at which the line is perceived to be aligned with gravity, can be found by presenting lines at different angles and asking the participant whether the line is rotated clockwise or counter-clockwise relative to gravity (see \panelref{intro:fig5}{A}).

When seated straight this task, participants do not make any static errors and are very certain about their responses (see \panelref{intro:fig5}{B} and \hyperref[intro:fig5]{C}). This changes when tilting the participant before the task. In general, the static error increases with tilt angle. When the direction of the error is in the direction of the body mid-line, this effect is known as the Aubert or A-effect \cite{aubert1861}. At smaller angles overcompensation occurs and the static error is in the opposite direction, which is away from the body mid-line. This latter effect is known as the E-effect and could be due to the effects of ocular counter-roll (OCR).

@@

We start with \Chapter{p1} in which we investigate sensory noise levels of the visual, somatosensory, and vestibular cues to spatial orientation. Because the contributions of these signals cannot be studied in isolation, we adopted an inverse approach where we assumed statistical optimality and attempted to compute the statistical properties of individual sensors. To this end, we fitted an optimal integration model to the behaviour from two psychophyisical tasks. The first gauged head-in-space orientation (SVV) and the second body-in-space orientation (SBT). The resulting estimates of the noise levels in the involved sensory modalities were used to predict the responses of patients with somatosensory and vestibular deficits. These predictions were consistent with previously published deficits in these patient groups, strengthening the idea that human spatial orientation is statistically optimal.

### 2015-04-17 src/misc/s3_summary.tex
Minor updates

Summary

>>>>

Navigeren door de omgeving oproept complexe veranderingen van visuele, auditieve, vestibulaire, tactiele en
motor inputs naar de hersenen. Toch, ondanks deze beweging veroorzaakte veranderingen van de input, we de wereld waarnemen als een stabiele werkelijkheid, maar ook een geïntegreerde gevoel van waar we zijn, hoe we zijn gericht, en in staat zijn op te sporen en te handelen in plaats moeiteloos op omliggende objecten. Hoe dit vermogen komt is ook het onderwerp van dit proefschrift. Het doel van het onderzoek beschreven in dit proefschrift was om computationele modellen op te bouwen en uit te voeren grondige psychometrische tests om de fysische en biologische beperkingen te ontrafelen op de interactie tussen het evenwichtsorgaan en andere sensorische systemen voor ruimtelijke oriëntatie en zelf-waarneming van beweging. Dit resulteerde in de volgende bijdragen aan het veld:

\ Begin {description}
\ Item [\ hoofdstuk {p1}] Statistische optimaliteit kan goed zijn voor de manier waarop het lichaam somatosensorische, zijn nek proprioceptieve en vestibulaire signalen geïntegreerd in ruimtelijke oriëntatie waarneming. Hoewel deze sensoren niet afzonderlijk kan worden onderzocht door optimaliteit als uitgangspunt geluidsemissie eigenschappen kunnen worden bepaald en gekoppeld aan klinische afwijkingen die worden gezien name patiëntengroepen.
\ Item [\ hoofdstuk {p3}] oogmotorische signalen beïnvloeden eigen waarneming van beweging, zelfs in afwezigheid van optic flow of andere visuele stimulatie, en zelfs in strijd met vestibulaire informatie.
\ Item [\ hoofdstuk {p4}] Dit oculomotorische signalen moet zo rudimentair cue om zelf-waarneming van beweging worden beschouwd; Het is niet veridically geschaald fixatie afstand in de perceptie van lichaam vertaling.
\ Item [\ hoofdstuk {p2}] Self-motion signalen interactie met de dynamische perceptie van de buitenwereld. Fouten die zich voordoen bij deze werkwijze suggereren het gebruik van een blik gecentreerd referentieframes in de onderliggende berekeningen.
\ End {description}

In de volgende paragrafen zullen we een gedetailleerd overzicht van elk resultaat te bieden.

\ Section {Multisensorische verwerking in ruimtelijke oriëntatie}
Vele studies hebben aangetoond dat de hersenen combineert luidruchtige sensorische signalen in een statistisch optimale wijze. Dit gebeurt normaal door te laten zien dat het geluidsniveau van elke afzonderlijke modaliteit prestaties in combinatie kunnen voorspellen. In ruimtelijke oriëntatie is het moeilijk om zintuiglijke signalen afzonderlijk te meten als men niet kan uitschakelen het vestibulair gevoel bij het meten van somatosensorische bijdragen. In \ hoofdstuk {p1} daarom gebruikten we een statistisch optimale integratie-model als uitgangspunt, en geprobeerd om rekening te houden met de perceptuele verschillen gevonden wanneer indringende kop-in-ruimte versus body-in-ruimte oriëntatie. Met een psychometrische benadering, testten we zowel de perceptie van lichaam tilt (persoonlijke gesl; SBT) en de waarneming van visuele verticale (subjectieve visuele verticaal, SVV) in zeven deelnemers. Omdat zowel de SVV en SBT maken gebruik van dezelfde zintuiglijke signalen, waren we in staat om een ​​7-parameter probabilistische model past bij de respons gegevens. Een van de geschatte parameters vertegenwoordigde het lawaai van de nek proprioceptoren. Dit liet ons toe om onafhankelijk te bevestigen dat de verkregen waarden voor de hals geluid overeen met die die werden gemeten in isolement. We verder gevalideerd ons model door te laten zien dat voorspellingen van ons model zijn in overeenstemming met eerder gepubliceerde tekorten in vestibulair en somatosensorische patiënten. We concluderen dat de Bayesiaanse berekeningen kan goed zijn voor de typische verschillen in ruimtelijke oriëntatie oordelen in verband met verschillende vereisten van de taak. In een vervolg op dit werk, werd deze aanpak onlangs toegepast op een patiëntenpopulatie met complete vestibulair verlies \ cite {alberts2015}. Prestaties in die patiënten vergelijkbaar met die van de controles, wat suggereert dat de sensorische gewicht was verschoven van de vestibulaire de somatische sensors.

\ Section {Oogbewegingen beïnvloeden zelf-waarneming van beweging}
Eye movement begeleiden meestal zelf-beweging om het netvlies slip minimaliseren en maximaliseren dynamische gezichtsscherpte. In \ hoofdstuk {p3} hebben we onderzocht of deze oogbewegingen hebben ook een omgekeerde rol, door te dienen als een cue voor zelf-waarneming van beweging. Om deze vraag te beantwoorden, vroegen we de deelnemers om gepercipieerde vertaling afstanden vergelijken van twee opeenvolgende, passieve, laterale hele lichaam vertalingen. Oogbewegingen tijdens deze vertalingen waren ofwel wereld-stationaire of body-stationaire. Resultaten laten zien dat de vertalingen korter werden waargenomen met body-fixed blik in vergelijking met-wereld vaste blik, wat aangeeft dat de oogbewegingen inderdaad beïnvloeden self-waarneming van beweging. Met behulp van een lineair model, schatten we de relatieve bijdrage van de vestibulaire versus de oogbeweging gebaseerd verplaatsingssignaal: de oogbeweging gebaseerd verplaatsingssignaal draagt ​​ongeveer 25 procent tot de waargenomen beweging. We onafhankelijk gevalideerd het model door het succes voorspellen van de effecten van oogbewegingen op zelf-waarneming van beweging tijdens de studies waarin de oogbewegingen waren ongedwongen. Dit toont verder dat oogbeweging signalen beïnvloeden eigen waarneming van beweging, zelfs zonder visuele stimulatie, en zelfs wanneer oculomotorische en vestibulaire schattingen in conflict, zoals tijdens-orgaan vastgestelde blik. We veronderstellen dat de nadelige gevolgen van deze schijnbaar starre opstelling minimaal zijn onder natuurlijke omstandigheden, omdat de oogbewegingen en zelf-beweging sterk gecorreleerd zijn, en omdat de oogbewegingen worden meestal begeleid door veridical optic flow aanwijzingen om zelf-beweging.

\ Section {gedeeltelijke compensatie voor fixatie diepte in zelf-waarneming van beweging}
Als oogbewegingen worden gebruikt bij de schatting van zelf-motion magnitude dient de hersenen ook de bijbehorende fixatie diepte slaan bij een veridical vertaling schatting. De reden is dat de amplitude van deze oogbewegingen, voor dezelfde fysieke vertaling, afhankelijk van de diepte van fixatie: als verre fixeren ze kleiner dan wanneer de omgeving fixeren in de wereld. In \ hoofdstuk {p4} hebben we onderzocht of de hersenen neemt inderdaad fixatie diepte te houden bij het gebruik van oogbewegingen om zelf-waarneming van beweging te vergroten. De deelnemers moesten zelf-motion tijdens verschillende omstandigheden oogbewegingen in de afwezigheid van full-field optic flow oordelen. In een 2-AFC taak, vergelijkbaar met die gebruikt in \ hoofdstuk {p3} deelnemers aangegeven of de tweede van twee opeenvolgende passieve zijdelingse gehele lichaam vertalingen langer of korter dan de eerste was. Tijdens elke vertaling, deelnemers gefixeerd ofwel een in de buurt of ver weg doelgroep, die ofwel lichaams- of world-stationaire was. Resultaten laten zien dat de waargenomen vertalingen waren korter voor nabijgelegen-wereld vaste blik in vergelijking met verre-wereld vaste blik, wat aangeeft dat de oogbewegingen niet goed geschaald in zelf-waarneming van beweging. Samen met de observatie dat zelf-waarneming van beweging niet wordt beïnvloed door de diepte van een lichaam stationaire fixatie doelgroep, kunnen we concluderen dat de oogbewegingen zijn slechts een rudimentaire cue om zelf-beweging, met een compensatie voor fixatie diepte die gedeeltelijke op zijn best.

\ Section {Gaze-afhankelijke effecten in ruimtelijke updating}
De hersenen moet ook zelf-beweging signalen naar ego-centrische ruimtelijke voorstellingen van het milieu te werken. In \ hoofdstuk {p2} onderzoeken we hoe, en in welke mate, de hersenen integreert de verschillende self-motion signalen voor de ruimtelijke-update. Deelnemers werden heen en weer geslingerd zijwaarts terwijl blik gericht op een stationaire doelwit. Wanneer de beweging richting veranderde, werd een verwijzing doel, hetzij voor of achter de fixatie punt getoond. Half een cyclus later, bij de volgende omkering, testten we bijwerking van de verwijzingen locatie door te vragen de deelnemers om te beoordelen of een kort flitste sonde werd getoond aan de linker- of rechterkant van de opgeslagen doel. De resultaten tonen aan dat zowel de richting en grootte van de bias in ruimtelijke bijwerking afhankelijk van de locatie van het object wordt geactualiseerd ten opzichte blik, hetgeen impliceert dat een blik centered referentiekader betrokken. We tonen verder aan dat deze vertekeningen kunnen worden veroorzaakt door een onderschat vertaling amplitude, een voorspanning van visueel waargenomen objecten naar de fovea, of door een combinatie van beide.

\ Section {Slotopmerkingen}

Alle experimentele hoofdstukken in dit proefschrift verslag over ruimtelijke beleving onderwerpen '. In \ hoofdstuk {p1} gebruiken we een optimale statistische integratiemodel van alle bijdragen sensorische systemen om zowel de bias en de precisie van deze waarnemingen te verklaren. In deze modellen de bijdragen van de zintuigen worden gewogen op basis van hun onzekerheid. In de hoofdstukken over laterale verplaatsing perceptie (\ hoofdstuk {p3, p4}) gebruiken we ook de wegingen van het evenwichtsorgaan en oog-beweging gebaseerde ramingen van de verplaatsing. Echter, deze weegt slechts op basis van de waargenomen biases in zelf-waarneming van beweging. Idealiter zou men dezelfde aanpak als in \ hoofdstuk {p1} te modelleren en analyseren van deze zelf-waarneming van beweging gegevens. We hebben eerste pogingen om een ​​dergelijke model gemaakt, maar verschijnen er tenminste twee belangrijke uitdagingen. Ten eerste, de geometrie van de zelf-waarneming van beweging experimenten maakt dat de eenvoudige Gauss uitkeringen van de ruimtelijke oriëntatie model te worden minder goed gedefinieerd, een scheve verdeling en we zouden moeten gebruiken roetfilter modellen om onze simulaties uit te voeren. Tweede, die modellen bevatten veel vrije parameters voor de zintuiglijke modaliteiten en priors. Met de huidige reeks experimenten we niet genoeg data om deze parameter te passen op een consistente manier te hebben. Toekomstig onderzoek moet worden gedaan om een ​​complete optimale rekening integratie van zelf-waarneming van beweging af te leiden.

In \ hoofdstuk {p2} laten we zien dat oogbewegingen uitgelokt door het fixeren van een wereld-stationaire doelwit worden in aanmerking genomen bij het updaten van de herinnerde locatie van eerder gezien doelen. Als de onderliggende signalen gebruikt voor zelf-waarneming van beweging zoals gevonden in \ hoofdstuk {p3, p4} worden ook gebruikt voor ruimtelijke bijwerken, het soort fixatie (wereld- versus body-stationaire) een effect op de waargenomen biases in ruimtelijke actualisering zou moeten hebben ook. Inderdaad, de resultaten van een proefproject in het vroege stadium van dit proefschrift suggereren dat Type fixatie beïnvloedt ruimtelijke bijwerken prestaties onder vertaling \ cite {clemens2010}. Deelnemers moesten bereiken richting herinnerde doelen na een tussenliggende vertaling. Voorlopige resultaten wijzen erop dat het bereiken van fouten zijn groot wanneer het fixeren van een body-stationaire doelwit tijdens de vertaling, terwijl er geen dergelijke fouten bestaan, terwijl het fixeren van wereldklasse stilstaande doelen \ cite {clemens2010}, wat suggereert dat inderdaad de eye-beweging gebaseerde self-motion signalen worden ook gebruikt in de ruimtelijke bijwerken.

Tot slot hoop ik nieuwe ontwikkelingen te hebben gemaakt in het begrip van de mechanismen voor ruimtelijke oriëntatie en zelf-waarneming van beweging. Natuurlijk, er zijn veel resterende vragen voor verdere studie. Deze onderzoeken moeten in de eerste plaats richten op de computationele en theoretische mechanismen, en hoe ze worden uitgevoerd door de neurale circuits. Deze studies moeten niet alleen het adres van de computationele en theoretische mechanismen, maar ook op de neurale implementatie en routes die kunnen worden gevonden in de hersenen.
